---
title: "Week 9 collaboration doc"
format: html
---

Read in packages

```{r}
library(tidyverse) # for data wrangling and plotting
library(ggeffects) # for model predictions
library(here) # for file pathing
library(lterdatasampler) # for data
```

Reading in data

```{r}
data(pie_crab) # reading in the Plum Island Ecosystem crab data
```

Exploratory vis

```{r}
pie_crab %>% 
  ggplot(aes(x=latitude, y=size)) + # initialize the plot
  geom_point(col = "orange") + # make a scatterplot, points orange
  labs(x = "Latitude", y = "Size (mm)") + # add informative labels
  theme_minimal() # remove gridlines, etc
```

How does latitude predict crab size?

```{r}
crab_model <- lm(size ~ latitude, # model formula
                 data = pie_crab) # data set
```

Check the diagnostics!

```{r}
par(mfrow = c(2, 2)) # displays diagnostics in a 2x2 grid
plot(crab_model) # plots diagnostic plots
```

We see: *homoscedastic residuals* (constant variance of residuals across the range of fitted = model predictions), *normally distributed residuals* (residuals follow the reference line in the QQ plot), *don't see outliers* (no points outside the dashed lines in the residuals vs leverage plot)

Look at the summary of our model!

```{r}
summary(crab_model) # look at model output
```

- slope = 0.49 plus minus 0.034
- y-intercept = -3.62 plus minus 1.27
- for each 1 degree increase in latitude, we expect an increase in crab size of 0.49 plus minus 0.034 mm

Model statistics: model statistics: (F(1, 390) = 208.5, p < 0.001, alpha = 0.05, R^2^ = 0.35)
